% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
% This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License.
% Modified by Zach Boyd. Further modified by Drake Brown.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage{etaremune}
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{textcomp}
\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
\usepackage{url}
\robustify\cftdotfill

%-----------------------------------------------------------
\setlength{\outerbordwidth}{3pt}
\definecolor{shadecolor}{gray}{0.75}
\definecolor{shadecolorB}{gray}{0.93}

%-----------------------------------------------------------
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
      \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[3]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#3} \\
  \end{tabular*}
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
    \textit{#2} & \\
\end{tabular*}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Drake B. Brown} & u1221123@umail.utah.edu \\
  PhD Student, Applied Mathematics & https://github.com/brownthesr \\
  Department of Mathematics & https://scholar.google.com/citations?user=BEqMd74AAAAJ \\
  University of Utah & \\
  2025 to present & \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

  \item
    \ressubheading{University of Utah}{Ph.D., Applied Mathematics}{2025--2029 (projected)}
    GPA 4.00 \\
    Advisor: Bao Wang \\
    Qualifying Exam Topics: ODEs, PDEs, Linear Models, Functional Analysis, Numerical Analysis

  \item
    \ressubheading{Brigham Young University}{B.S., Applied \& Computational Mathematics (ACME), CS Minor}{2021--2025}
    Major GPA 4.00 \\
    Concentration: Deep Learning \\
    Merit-based department scholarship \\
    Undergraduate Advisor: Zachary M. Boyd

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Primary Research Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item Generative modeling: flow matching, diffusion, score-based models, one-step generators, and steering pretrained generators via MCMC
    \item Geometric and equivariant deep learning; Neural ODEs for physical dynamical systems
    \item Graph neural networks: theory, expressivity, and equation-free methods on dynamic graphs
    \item Agentic systems: multi-agent dynamics, adversarial robustness, and Agent-as-a-Judge evaluation
    \item Optimal control and multi-agent coordination
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item \textbf{D. Brown}, T. Garrity, K. Parker, J. Oliphant, S. Carson, C. Hanson, Z. Boyd. ``Beyond Linear: A Theoretical and Empirical Analysis of Nonlinear GNNs for Community Detection.'' \textit{SIAM Journal on Applied Mathematics}, in press (2026). \textbf{First author.}
    \item S. H. Wang, J. Keller, T. Transue, D. B. Brown, T. Strohmer, B. Wang. ``Test-Time Guidance for Flow-Based Generative Models via Parallel Tempering on Source Distributions.'' \textit{International Conference on Machine Learning (ICML)}, 2026. Accepted.
    \item \textbf{D. Brown}, T. Garrity, D. Perkins, D. Hunter, W. Pochman. ``Optimal Control Strategies for Multi-Agent Sheep Herding.'' arXiv:2510.25115, 2025. \textbf{First author.}
    \item \textbf{D. Brown}, D. Perkins, D. Hunter, T. Garrity, W. Pochman. ``Explorations of Epidemiological Dynamics across Multiple Population Hubs.'' arXiv:2510.25085, 2025. \textbf{First author.}
    \item Manuscript under review at \textit{NeurIPS} 2026.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \ressubheading{Ph.D. Researcher}{University of Utah, Department of Mathematics}{2025--present}
    \begin{itemize}
        \item Accelerated training methods for one-step generative models with provable convergence guarantees
        \item Test-time steering of pretrained flow-based generators via parallel-tempering MCMC over source latents
        \item Equivariant Neural ODEs for chaotic gravitational dynamics (three-body problem)
    \end{itemize}

    \item \ressubheading{Lead Research Assistant}{Graph Neural Networks Lab, BYU}{2022--2025}
    \begin{itemize}
        \item Theoretical and empirical analysis of nonlinear GNNs for community detection (\textit{SIAM J. Appl. Math.})
        \item Equation-free graph neural networks for forecasting epidemic dynamics on adaptive contact networks
        \item Led parallel experimentation training 200+ GNN models, generating 15M+ data points (PyTorch)
    \end{itemize}

    \item \ressubheading{Computer Vision Research Intern}{Air Force Research Laboratory}{Summer 2023}
    \begin{itemize}
        \item Implemented momentum-based self-supervised vision models (BYOL, DINO) in PyTorch
        \item Outperformed state-of-the-art on STL-10 and CIFAR-100 by 4\% on linear-probe accuracy
    \end{itemize}

    \item \ressubheading{Research Assistant}{Perception, Cognition and Control Lab, BYU}{2022--2023}
    \begin{itemize}
        \item Probed what large language models encode about societal issues (inequality, racism) through generated narratives, using demographic-conditioned prompts to elicit first-person stories of observing or experiencing these phenomena
        \item Built an analysis pipeline embedding generated stories with sentence transformers and clustering in latent space, surfacing underlying patterns in how models represent these issues across demographic groups
    \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Industry Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \ressubheading{Applied Scientist Intern}{Kiro Science, AWS \textbullet{} Santa Clara, CA}{May--Aug 2026}
    \begin{itemize}
        \item Designing a self-improving multi-agent adversarial framework for measuring Agent-as-a-Judge robustness
        \item Taxonomizing attack-class biases and evaluating cross-model judge vulnerability transfer
    \end{itemize}

    \item \ressubheading{Software Engineering Intern}{API Gateway, AWS \textbullet{} Denver, CO}{Jun--Aug 2024; May--Aug 2025}
    \begin{itemize}
        \item Re-architected Private API ingress by removing the NGINX proxy layer in favor of direct traffic handling in Protocol Service
        \item Designed and deployed an isolation fleet to mitigate large-scale DDoS attacks across 300K+ accounts
        \item Reduced p99 latency from 2000\,ms to 20\,ms under adversarial load; increased successful API transactions by 30\%
    \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \textbf{Talks}
    \begin{etaremune}
        \item Connecting the Performance of Graph Neural Network Architectures to the Properties of Training Data, BYU Student Research Conference, February 2024.
        \item (Invited) Connecting the Performance of Graph Neural Network Architectures to the Properties of Training Data, $2^{\text{nd}}$ SIAM Northern States Section Conference, April 2023.
    \end{etaremune}
    \item \textbf{Posters}
    \begin{etaremune}
        \item Test-Time Guidance for Flow-Based Generative Models via Parallel Tempering on Source Distributions, \textit{International Conference on Machine Learning (ICML)}, 2026.
        \item Connecting the Performance of GNN Architectures to the Properties of Training Data, Northeast Regional Conference on Complex Systems, March 2023.
    \end{etaremune}
    \item \textbf{Accepted Abstracts}
    \begin{etaremune}
        \item Global Minima, Recoverability Thresholds, and Higher-Order Structure in GNNs, Conference on Complex Systems, October 2023.
    \end{etaremune}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Selected Coursework}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabularx}{6.5in}{XXX}
    Advanced Deep Learning              & Stochastic Differential Equations  & Mathematics of Deep Learning \\
    Linear \& Nonlinear Analysis        & Modeling with Uncertainty in Data  & Algorithm Design \& Optimization \\
    Dynamics \& Control Theory          & Advanced Programming Concepts      & \\
\end{tabularx}\vspace{4pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards and Honors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item Math Department Dean's List, BYU (2021--2024)
    \item Best Presentation Award, BYU Student Research Conference
    \item Outstanding Sophomore, BYU Mathematics Department
    \item Merit-based Department Scholarship, BYU Mathematics
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Programming and Development}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \textbf{Languages:} Python, C++, Java, Rust, SQL, Bash, \LaTeX, Git
    \item \textbf{Python Libraries:} PyTorch, PyTorch Lightning, PyTorch Geometric, NumPy, Pandas, NetworkX, Seaborn, Matplotlib
    \item \textbf{Research Areas:} Geometric Deep Learning, Generative Models, Graph Neural Networks, Neural ODEs, Optimal Control, Numerical Linear Algebra
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Citizenship}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
United States

\end{document}
