\documentclass[letterpaper,11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{parskip}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

% Section heading styling: small caps, rule underneath
\titleformat{\section}
  {\large\scshape\raggedright}
  {}{0em}
  {}[\vspace{-6pt}\titlerule\vspace{2pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% Tight lists
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt}
\setlist[enumerate]{leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt}

\pagestyle{empty}

% A small helper for two-column rows (left bold, right italic, right-aligned)
\newcommand{\entry}[4]{%
  \noindent\begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{#3} & #4 \\
  \end{tabularx}\vspace{2pt}
}

\begin{document}

%====== Header ======
\begin{center}
  {\LARGE \textbf{Drake Brown}}\\[2pt]
  \href{mailto:Drakebenbrown@gmail.com}{Drakebenbrown@gmail.com} \, \textbar\, \href{https://www.linkedin.com/in/drake-brown-5398b9224}{linkedin.com/in/drake-brown} \, \textbar\, \href{https://github.com/brownthesr}{github.com/brownthesr} \, \textbar\, \href{https://scholar.google.com/citations?user=BEqMd74AAAAJ}{Google Scholar}
\end{center}

%====== Education ======
\section*{Education}

\entry{PhD, Applied Mathematics}{April 2029}
      {University of Utah \, \textbullet\, Advisor: Bao Wang}{Salt Lake City, UT}
\vspace{-4pt}
\begin{itemize}
  \item Qualifying Exam Topics: ODEs, PDEs, Linear Models, Functional Analysis, Numerical Analysis
  \item GPA: 4.00
\end{itemize}

\entry{BS, Applied \& Computational Mathematics (ACME), CS Minor}{April 2025}
      {Brigham Young University \, \textbullet\, Concentration: Deep Learning}{Provo, UT}
\vspace{-4pt}
\begin{itemize}
  \item Major GPA: 4.00
  \item Relevant Coursework:
\end{itemize}
\vspace{-8pt}
\noindent\begin{tabularx}{\textwidth}{XXX}
  Advanced Deep Learning      & Mathematics of Deep Learning      & Stochastic Differential Equations \\
  Linear \& Nonlinear Analysis & Modeling with Uncertainty in Data & Algorithm Design \& Optimization \\
  Dynamics \& Control Theory   & Advanced Programming Concepts     & \\
\end{tabularx}

%====== Publications ======
\section*{Publications}

\begin{enumerate}
  \item \textbf{D.~Brown}, T.~Garrity, K.~Parker, J.~Oliphant, S.~Carson, C.~Hanson, Z.~Boyd. ``Beyond Linear: A Theoretical and Empirical Analysis of Nonlinear GNNs for Community Detection.'' \textit{SIAM Journal on Applied Mathematics}, in press (2026). \textbf{First author.}
  \item J.~Keller, \ldots, \textbf{D.~Brown}. ``Test-Time Guidance for Flow-Based Generative Models via Parallel Tempering on Source Distributions.'' \textit{International Conference on Machine Learning (ICML)}, 2026. Accepted.
  \item \textbf{D.~Brown}, T.~Garrity, D.~Perkins, D.~Hunter, W.~Pochman. ``Optimal Control for Multi-Agent Sheep Herding.'' \texttt{arXiv:2510.25115}, 2025. \textbf{First author.}
  \item \textbf{D.~Brown}, D.~Perkins, D.~Hunter, T.~Garrity, W.~Pochman. ``Epidemiological Dynamics across Multiple Population Hubs.'' \texttt{arXiv:2510.25085}, 2025. \textbf{First author.}
  \item Manuscript under review at \textit{NeurIPS} 2026.
\end{enumerate}

%====== Skills ======
\section*{Skills}

\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
  \textbf{Languages} & Python (PyTorch, Lightning, PyTorch Geometric, NumPy, Pandas), C++, Java, Rust, SQL, Bash \\
  \textbf{Topics}    & Generative Models, Graph Neural Networks, Neural ODEs, Equivariant Deep Learning, Optimal Control, Stochastic Differential Equations, Numerical Linear Algebra, Multi-Agent Systems \\
\end{tabularx}

%====== Experience ======
\section*{Experience}

\entry{AWS Applied Scientist Intern}{May -- August 2026}
      {Kiro Science, Amazon}{Santa Clara, CA}
\vspace{-4pt}
\begin{itemize}
  \item Designed and shipped a self-improving multi-agent adversarial framework for measuring Agent-as-a-Judge robustness; taxonomized 6 attack-class biases and demonstrated cross-model judge vulnerability transfer.
\end{itemize}

\entry{AWS Software Engineering Intern}{Jun--Aug 2024; May--Aug 2025}
      {API Gateway, Amazon}{Denver, CO}
\vspace{-4pt}
\begin{itemize}
  \item Re-architected Private API ingress by removing the NGINX proxy layer and implementing direct traffic handling
  \item Designed and deployed an isolation fleet to mitigate large-scale DDoS attacks across 300K+ accounts
  \item Increased successful API transactions by 30\% via dynamic routing and system-level optimization
  \item Reduced p99 latency from 2000\,ms to 20\,ms under adversarial load
\end{itemize}

\entry{Research Assistant Lead}{February 2022 -- April 2025}
      {Graph Neural Networks Lab \, \textbullet\, Brigham Young University}{Provo, UT}
\vspace{-4pt}
\begin{itemize}
  \item Led large-scale experimentation training 200+ GNN models in parallel (15M+ data points) using PyTorch
  \item Invited talk at SIAM-NSS; accepted paper to \textit{SIAM Journal on Applied Mathematics}
\end{itemize}

\end{document}
